How has the Amazon been construed as a problem? Preliminary Analysis

### 2022-04-06 analysis/analysis_livio.Rmd

amazon_def_year <- amazon_def_year %>% rename(def_year = "area km\u00b2")

@@

pop2 <- pop %>% count(amazon_speech, year, president) %>%
  group_by(year, president) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1) %>%
  mutate(election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))

@@

model <- lm(perc ~ AAI+ def_year + president + election_year, data=pop2)

@@

pop2 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(size=.65, aes(x=year, y=perc, color="real share"), linetype= "solid")+
  geom_line(size=.5, aes(x=year, y=predicted, color="Predicted share"), linetype="dotted")+
  scale_color_manual(values=c("real share"="darkolivegreen", "Predicted share"= "black"))+
  scale_y_continuous(labels = percent_format())+
  labs(
    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
    subtitle = "Sample composed by 6130 presidential speeches since 1985",
    caption = "Predicted share curve controls for yearly deforestation rates, yearly inflation, and president", color='Y series') +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "bottom"
  )

>>>>

@@

pop2 <- pop %>% count(amazon_speech, year, president) %>%
  group_by(year, president) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1)

@@

model <- lm(perc ~ AAI+ def_year + president, data=pop2)

@@

pop2 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(size=.75, aes(x=year, y=perc, color="real share"), linetype= "solid")+
  geom_line(size=.5, aes(x=year, y=predicted, color="Predicted share"), linetype="solid")+
  scale_color_manual(values=c("real share"="darkolivegreen", "Predicted share"= "black"))+
  scale_y_continuous(labels = percent_format())+
  labs(
    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
    subtitle = "Sample composed by 6130 presidential speeches since 1985",
    caption = "Predicted share curve controls for yearly deforestation rates, yearly inflation, and president", color='Y series') +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "bottom"
  )
